---
title: "ContractTermination"
author: "Greg Sanders"
date: "Wednesday, February 8, 2017"
output:
  html_document:
    keep_md: yes
--- 

Is Terminated exploration
============================================================================

#Setup
```{r InputFiles, echo = TRUE}
Path<-"C:\\Users\\gsand_000.ALPHONSE\\Documents\\Development\\R-scripts-and-data\\"
# Path<-"D:\\Users\\Greg Sanders\\Documents\\Development\\R-scripts-and-data\\"
# Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(file.path(Path,"lookups.r",sep=""))
source(file.path(Path,"helper.r",sep=""))

source("ContractCleanup.r")
library(csis360)
library(ggplot2)
library(scales)
library(Hmisc)
library(plyr)
Coloration<-read.csv(
    paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
    header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
    stringsAsFactors=FALSE
    )

Coloration<-ddply(Coloration
                  , c(.(R), .(G), .(B))
                  , transform
                  , ColorRGB=as.character(
                      if(min(is.na(c(R,G,B)))) {NA} 
                      else {rgb(max(R),max(G),max(B),max=255)}
                      )
                  )


axis.text.size<-10
strip.text.size<-10
legend.text.size<-8
# table.text.size<-5.75
title.text.size<-12
geom.text.size<-12

main.text.size<-1
note.text.size<-1.40


```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations


Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  


##Prepare Data

```{r ReadInData, echo = TRUE}
  load(file="LargeDataSets/Federal_contract_CSIScontractID_detail.Rdata")
head(FederalModelAndDetail)
```

```{r PrepareData}


#ContractWeighted <- apply_lookups(Path,ContractWeighted)


FederalModelAndDetail$TermNum<-as.integer(as.character(factor(FederalModelAndDetail$Term,
                                  levels=c("Terminated","Unterminated"),
                                  labels=c(1,0))))

FederalModelAndDetail$ObligationWT<-FederalModelAndDetail$Action.Obligation
FederalModelAndDetail$ObligationWT[FederalModelAndDetail$ObligationWT<0]<-NA

# FederalModelAndDetail<-ddply(FederalModelAndDetail,
#                          .(Ceil),
#                          
#                          plyr::mutate,
#                          ceil.median.wt = median(UnmodifiedContractBaseAndAllOptionsValue)
# )


FederalModelAndDetail$UnmodifiedYearsFloat<-FederalModelAndDetail$UnmodifiedDays/365.25
FederalModelAndDetail$UnmodifiedYearsCat<-floor(FederalModelAndDetail$UnmodifiedYearsFloat)
FederalModelAndDetail$Dur[FederalModelAndDetail$UnmodifiedYearsCat<0]<-NA

FederalModelAndDetail$Dur.Simple<-as.character(FederalModelAndDetail$Dur)
FederalModelAndDetail$Dur.Simple[FederalModelAndDetail$Dur.Simple %in% c(
    "[0 months,~2 months)",
    "[~2 months,~7 months)",
    "[~7 months-~1 year]")]<-"<~1 year"
FederalModelAndDetail$Dur.Simple<-factor(FederalModelAndDetail$Dur.Simple,
                                          levels=c("<~1 year",
                                               "(~1 year,~2 years]",
                                               "(~2 years+]"),
                                   ordered=TRUE
                                   )

FederalModelAndDetail$Ceil.Simple<-as.character(FederalModelAndDetail$Ceil)

FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "75m+",
    "[75m+]",
    "[10m,75m)",
    "10m - <75m"
    )]<-"10m+"
FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "1m - <10m",
    "[1m,10m)",
    "100k - <1m",
    "[100k,1m)",
    "[100k,1m)"
    )]<-"100k - <10m"
FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "15k - <100k",
    "[15k,100k)",
    "0 - <15k",
    "[0,15k)")]<-"0k - <100k"
FederalModelAndDetail$Ceil.Simple<-factor(FederalModelAndDetail$Ceil.Simple,
       levels=c("0k - <100k",
                "100k - <10m",
                "10m+"),
       ordered=TRUE
       )

FederalModelAndDetail$DecisionTree<-as.character(FederalModelAndDetail$MaxOfDecisionTree)
FederalModelAndDetail$DecisionTree[
  FederalModelAndDetail$DecisionTree=="Excluded"|
    is.na(FederalModelAndDetail$DecisionTree)]<-"All Other"
FederalModelAndDetail$DecisionTree<-factor(FederalModelAndDetail$DecisionTree,levels=c("OCO","Disaster","ARRA","All Other"))

if(!"Is.Defense" %in% colnames(FederalModelAndDetail)){
  FederalModelAndDetail$Is.Defense<-as.character(FederalModelAndDetail$Who)
  FederalModelAndDetail$Is.Defense[FederalModelAndDetail$Is.Defense %in%
                                     c("Air Force","Army",
                                       "Navy","Other DoD","Uncategorized"  )
                                   ]<-"Defense"
  FederalModelAndDetail$Is.Defense<-factor(FederalModelAndDetail$Is.Defense)
}




 FederalModelAndDetail$DecisionTreeDisplay<-as.character( FederalModelAndDetail$DecisionTreeDisplay)

FederalModelAndDetail$DecisionTreeDisplay[
<<<<<<< HEAD
                                      (FederalModelAndDetail$StartFiscalYear<=2011 |
                                          FederalModelAndDetail$StartFiscalYear>2016
                                      ) &
=======
                                      (FederalModelAndDetail$StartFiscalYear<=2011 | 
                                         FederalModelAndDetail$StartFiscalYear>2016 )&
>>>>>>> 7a20786559540068f76d32f9d268ba0fe009ebc1
                                      FederalModelAndDetail$DecisionTree=="OCO"]<-"Not in Sample"
FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$StartFiscalYear>=2012 &
                                      FederalModelAndDetail$StartFiscalYear<=2016 &
                                      FederalModelAndDetail$DecisionTree=="OCO"]<-
  "OCO ('12+)"
FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="Disaster"&
                                        FederalModelAndDetail$StartFiscalYear>=2007]<-"Disaster ('07+)"
FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="Disaster"&
                                        FederalModelAndDetail$StartFiscalYear<2007]<-"Not in Sample"
FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="ARRA"]<-"ARRA ('09-'13)"

FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="All Other" &
                                      FederalModelAndDetail$Intl=="Just U.S." &
                                      FederalModelAndDetail$Is.Defense=="Civilian"
                                      ]<-"Other U.S. Civilian ('07+)"

FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="All Other" &
                                      FederalModelAndDetail$Intl=="Any Intl" &
                                      FederalModelAndDetail$Is.Defense=="Civilian"
                                      ]<-"Other Intl. Civilian ('07+)"

FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="All Other" &
                                      FederalModelAndDetail$Intl=="Just U.S." &
                                      FederalModelAndDetail$Is.Defense=="Defense" &
                                        FederalModelAndDetail$StartFiscalYear>=2012 &
                                      FederalModelAndDetail$StartFiscalYear<=2016
                                      ]<-"Other U.S. Defense ('12+)"

FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="All Other" &
                                      FederalModelAndDetail$Intl=="Any Intl" &
                                      FederalModelAndDetail$Is.Defense=="Defense" & 
                                      FederalModelAndDetail$StartFiscalYear>=2012 &
                                      FederalModelAndDetail$StartFiscalYear<=2016 
                                      ]<-"Other Intl. Defense ('12+)"

FederalModelAndDetail$DecisionTreeDisplay[FederalModelAndDetail$DecisionTree=="All Other" &
                                      FederalModelAndDetail$Is.Defense=="Defense" & 
                                      FederalModelAndDetail$StartFiscalYear<=2011 
                                      ]<-"Not in Sample"

FederalModelAndDetail$DecisionTreeDisplay[(FederalModelAndDetail$Intl=="Unlabeled") |
                                            is.na(FederalModelAndDetail$Is.Defense) &
                                            FederalModelAndDetail$DecisionTree=="All Other" 
                                      ]<-"Not in Sample"
  
FederalModelAndDetail$DecisionTreeDisplay<-factor(FederalModelAndDetail$DecisionTreeDisplay)

summary(FederalModelAndDetail$DecisionTreeDisplay)
# FederalModelAndDetail<-subset(FederalModelAndDetail,DecisionTreeDisplay != "Not in Sample")
# save(complete_FederalModelAndDetail,FederalModelAndDetail,file="data//FederalModelAndDetail.Rdata")

View(FederalModelAndDetail[is.na(FederalModelAndDetail$DecisionTreeDisplay),])


summary(FederalModelAndDetail$DecisionTree)
summary(FederalModelAndDetail$DecisionTreeDisplay)
write.csv(subset(FederalModelAndDetail,Term=="Terminated"),"LargeDataSets//Terminated.csv")

save(FederalModelAndDetail,file="LargeDataSets//FederalModelForTerminations.RData")


```


#Analysis

##Data preparation
```{r SDurSCeilCount, fig.width=6.5,fig.height=5, dpi=600}
# load(file="LargeDataSets//FederalModelForTerminations.RData")
TerminatedSDurSCeilStatCount<-ddply(
  subset(FederalModelAndDetail,
         !is.na(Dur.Simple) & 
           !is.na(Ceil.Simple) &
           !is.na(Term) &
      DecisionTreeDisplay != "Not in Sample" &
           StartFiscalYear>=2007 & 
<<<<<<< HEAD
           StartFiscalYear<=2015 
=======
           StartFiscalYear<=2015 &
           (DecisionTreeDisplay != "Not in Sample")
>>>>>>> 7a20786559540068f76d32f9d268ba0fe009ebc1
  ),
  # &                
           #     (LastCurrentCompletionDate<=as.Date("2015-09-30") |
           #          IsClosed==1) &
           #     UnmodifiedCurrentCompletionDate<as.Date("2015-09-30")),
    .(Dur.Simple,
      Ceil.Simple,
      # StartFiscalYear,
      Term,
      DecisionTreeDisplay,
      # Is.Defense,
      # Intl,
      SingleOffer,
      UCA
    ),
    plyr::summarise,
    Action.Obligation=sum(Action.Obligation),
    Count=length(CSIScontractID),
    metric="Contracts within Period"
)


save(TerminatedSDurSCeilStatCount,file="TerminatedSDurSCeilStatCount.Rdata")
load(file="TerminatedSDurSCeilStatCount.Rdata")

TerminatedSDurSCeilStatCount$Term<-factor(TerminatedSDurSCeilStatCount$Term,
                                          levels=c("Unterminated",
                                                   "Terminated"),
                                          labels=c("Unterminated",
                                                   "Complete or Partial Termination"),
                                            ordered=TRUE)


TerminatedSDurSCeilLabels<-ddply(
    TerminatedSDurSCeilStatCount,
    .(Dur.Simple,Ceil.Simple),
    plyr::summarise,
    FacetCount=paste("Count:",prettyNum(sum(Count),big.mark=",")),
    FacetValue=paste(FacetCount,"\nObligated: $",round(sum(Action.Obligation)/1000000000,1),"B",sep="")
    )


TerminatedSDurSCeilStatCount$DecisionTreeDisplay<-factor(TerminatedSDurSCeilStatCount$DecisionTreeDisplay,
  levels(dtd_colors$variable),
  ordered=TRUE)



# debug(LatticePlotWrapper)
# top_line_term<-LatticePlotWrapper(
#   VAR.color.legend.label="Classification",
#   VAR.main.label="",
#   VAR.X.label="Fiscal Year",
#   VAR.Y.label="Constant ($ Billions)",
#   VAR.Coloration=Coloration,
#   VAR.long.DF=TerminatedSDurSCeilStatCount,
#   # NA, #VAR.ncol
#   VAR.x.variable="StartFiscalYear", #VAR.x.variable
#   VAR.y.variable="Count", #VAR.y.variable
#   VAR.y.series="Term", #VAR.y.series
#   VAR.facet.primary="Dur.Simple", #VAR.facet.primary
#   VAR.facet.secondary= "Ceil.Simple", # VAR.facet.secondary=NA
#   # ,MovingAverage=0
#   # ,MovingSides=1
#   DataLabels=FALSE
#   #                       ,VAR.override.coloration=NA
# )+geom_text(data=TerminatedSDurSCeilLabels,
#               aes(x=2007,y=Ypos,label=FacetValue),
#               # parse=TRUE,
#               hjust=0,
#               vjust=1,
#               color="black")
```

##Top Line Terminations
```{r Top_Line_Term}
top_line_term_data<-ddply(
    TerminatedSDurSCeilStatCount,
      .(Dur.Simple,
      Ceil.Simple,
      # StartFiscalYear,
      Term,
      DecisionTreeDisplay
      # Who,
      # Intl,
      # SingleOffer,
      # UCA,
    ),
    plyr::summarise,
    Action.Obligation=sum(Action.Obligation),
    Count=sum(Count)
)


top_line_term_data<-ddply(
    top_line_term_data,
      .(Dur.Simple,
      Ceil.Simple,
      DecisionTreeDisplay
    ),
    plyr::mutate,
    pObligation=Action.Obligation/sum(Action.Obligation),
    pCount=Count/sum(Count)
)

Ypos<-max(subset(top_line_term_data,Term=="Complete or Partial Termination")$pCount)*2
Xpos<-levels(top_line_term_data$DecisionTreeDisplay)[[1]]



dtd_colors$variable
levels(TerminatedSDurSCeilStatCount$DecisionTreeDisplay)
<-prepare_labels_and_colors(top_line_term_data,"DecisionTreeDisplay")

top_line_term<-ggplot(subset(top_line_term_data,Term=="Complete or Partial Termination"),
                    aes(x=DecisionTreeDisplay,y=pCount))+
    geom_bar(stat="identity", aes(fill=DecisionTreeDisplay))+
    # geom_line(aes(group=DecisionTreeDisplay,size=0.5))+
  # geom_point(aes(x=DecisionTreeDisplay,y=pCount))+
    geom_text(data=TerminatedSDurSCeilLabels,
              aes(x=Xpos,y=Ypos,label=FacetValue),
              # parse=TRUE,
              hjust=0,
              vjust=1,
              color="black")+
    facet_grid( Dur.Simple ~ Ceil.Simple  ) +#
    scale_x_discrete("Crisis Funding or Comparison Group")+
    # scale_color_manual("Status", values=c("blue","red"))+
    # scale_linetype_discrete("Early Results")+
    scale_shape_discrete("Status")+
    # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1)+
    theme(legend.position="none")+
  scale_fill_manual(
        "Crisis or Comparison Dataset"
        ,  values=c(dtd_colors$RGB)
        , limits=c(dtd_colors$variable)
        , labels=c(dtd_colors$Label)
        
    )+ theme(axis.text.x = element_text(angle=90))+
    scale_y_continuous("Percent Terminated", labels = percent_format())+
 theme(strip.text.y = element_text(angle=0))
  
 


top_line_term
ggsave("Output//top_line_term.png",top_line_term, width=6.5, height= 5, units="in",dpi=300)

```

```{r Comp_Term}
summary(TerminatedSDurSCeilStatCount$SingleOffer)
TerminatedSDurSCeilStatCount$SingleOffer<-as.character(TerminatedSDurSCeilStatCount$SingleOffer)
TerminatedSDurSCeilStatCount$SingleOffer[TerminatedSDurSCeilStatCount$SingleOffer=="None or Unlabeled"]<-NA
TerminatedSDurSCeilStatCount$SingleOffer[TerminatedSDurSCeilStatCount$SingleOffer=="Single"]<-"None/1 Offer"
comp_term_data<-ddply(
    subset(TerminatedSDurSCeilStatCount,!is.na(SingleOffer)),
      .(Dur.Simple,
      Ceil.Simple,
      # StartFiscalYear,
      Term,
      DecisionTreeDisplay,
      # Who,
      # Intl,
      SingleOffer
      # UCA,
    ),
    plyr::summarise,
    Action.Obligation=sum(Action.Obligation),
    Count=sum(Count)
)

comp_term_data<-ddply(
    comp_term_data,
      .(Dur.Simple,
      Ceil.Simple,
      DecisionTreeDisplay,
	  SingleOffer
    ),
    plyr::mutate,
    pObligation=Action.Obligation/sum(Action.Obligation),
    pCount=Count/sum(Count)
)

Ypos<-max(subset(comp_term_data,Term=="Complete or Partial Termination")$pCount)*1.5
Xpos<-levels(comp_term_data$DecisionTreeDisplay)[[1]]

# 
# comp_term<-ggplot(subset(comp_term_data,Term=="Complete or Partial Termination"),
#                     aes(x=DecisionTreeDisplay,y=pCount,color=DecisionTreeDisplay))+
#     geom_bar(stat="identity")+
#     # geom_line(aes(group=DecisionTreeDisplay,size=0.5))+
#   geom_point(aes(x=DecisionTreeDisplay,y=pCount))+
#     # geom_text(data=TerminatedSDurSCeilLabels,
#     #           aes(x=Xpos,y=Ypos,label=FacetValue),
#     #           # parse=TRUE,
#     #           hjust=0,
#     #           vjust=1,
#     #           color="black")+
#     facet_grid( Comp + Dur.Simple ~ Ceil.Simple  ) +#
#     scale_x_discrete("Crisis Funding or Comparison Group")+
#     # scale_color_manual("Status", values=c("blue","red"))+
#     # scale_linetype_discrete("Early Results")+
#     scale_shape_discrete("Status")+
#     scale_y_continuous("Percent Terminated",label=comma)+
#     # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1)+
#     theme(legend.position="bottom") #, position=pd


comp_term<-ggplot(subset(comp_term_data,Term=="Complete or Partial Termination"),
                    aes(x=DecisionTreeDisplay,y=pCount))+
    geom_bar(stat="identity", aes(fill=DecisionTreeDisplay))+
    # geom_line(aes(group=DecisionTreeDisplay,size=0.5))+
  # geom_point(aes(x=DecisionTreeDisplay,y=pCount))+
    # geom_text(data=TerminatedSDurSCeilLabels,
    #           aes(x=Xpos,y=Ypos,label=FacetValue),
    #           # parse=TRUE,
    #           hjust=0,
    #           vjust=1,
    #           color="black")+
    facet_grid( SingleOffer + Dur.Simple ~ Ceil.Simple  ) +#
    scale_x_discrete("Crisis Funding or Comparison Group")+
    # scale_color_manual("Status", values=c("blue","red"))+
    # scale_linetype_discrete("Early Results")+
    scale_shape_discrete("Status")+
    # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1)+
    theme(legend.position="none")+
  scale_fill_manual(
        "Crisis or Comparison Dataset"
        ,  values=c(dtd_colors$RGB)
        , limits=c(dtd_colors$variable)
        , labels=c(dtd_colors$Label)
        
    )+ theme(axis.text.x = element_text(angle=90))+
    scale_y_continuous("Percent Terminated", labels = percent_format())+
 theme(strip.text.y = element_text(angle=0))
  
 
ggsave("Output//comp_term.png",comp_term, width=6.5, height= 7, units="in",dpi=300)

dtd_colors$variable
levels(TerminatedSDurSCeilStatCount$DecisionTreeDisplay)
# TerminatedSDurSCeilStatCount$DecisionTreeDisplay<-
#   factor(TerminatedSDurSCeilStatCount$DecisionTreeDisplay,
#     levels=c(                  "Disaster ('07+)",             "ARRA ('09-'13)" ,"OCO ('12+)",
# "Other U.S. Civilian ('07+)",  "Other Intl. Civilian ('07+)" ,"Other U.S. Defense ('12+)"  ,
# "Other Intl. Defense ('07+)", "Not in Sample"
# ))

comp_term
```


##UCA
```{r UCA_Term}
uca_term_data<-ddply(
    subset(TerminatedSDurSCeilStatCount,!is.na(UCA)),
      .(Dur.Simple,
      Ceil.Simple,
      # StartFiscalYear,
      Term,
      DecisionTreeDisplay,
      # Who,
      # Intl,
      # SingleOffer,
      UCA
    ),
    plyr::summarise,
    Action.Obligation=sum(Action.Obligation),
    Count=sum(Count)
)

uca_term_data<-ddply(
    uca_term_data,
      .(Dur.Simple,
      Ceil.Simple,
      DecisionTreeDisplay,
	  UCA
    ),
    plyr::mutate,
    pObligation=Action.Obligation/sum(Action.Obligation),
    pCount=Count/sum(Count)
)

Ypos<-max(subset(uca_term_data,Term=="Complete or Partial Termination")$pCount)*1.5
Xpos<-levels(uca_term_data$DecisionTreeDisplay)[[1]]


uca_term<-ggplot(subset(uca_term_data,Term=="Complete or Partial Termination"),
                    aes(x=DecisionTreeDisplay,y=pCount))+
    geom_bar(stat="identity", aes(fill=DecisionTreeDisplay))+
    # geom_line(aes(group=DecisionTreeDisplay,size=0.5))+
  # geom_point(aes(x=DecisionTreeDisplay,y=pCount))+
    # geom_text(data=TerminatedSDurSCeilLabels,
    #           aes(x=Xpos,y=Ypos,label=FacetValue),
    #           # parse=TRUE,
    #           hjust=0,
    #           vjust=1,
    #           color="black")+
    facet_grid( UCA + Dur.Simple ~ Ceil.Simple  ) +#
    scale_x_discrete("Crisis Funding or Comparison Group")+
    # scale_color_manual("Status", values=c("blue","red"))+
    # scale_linetype_discrete("Early Results")+
    scale_shape_discrete("Status")+
    # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1)+
    theme(legend.position="none")+
  scale_fill_manual(
        "Crisis or Comparison Dataset"
        ,  values=c(dtd_colors$RGB)
        , limits=c(dtd_colors$variable)
        , labels=c(dtd_colors$Label)
        
    )+ theme(axis.text.x = element_text(angle=90))+
    scale_y_continuous("Percent Terminated", labels = percent_format())+
 theme(strip.text.y = element_text(angle=0))
  
 uca_term
ggsave("Output//uca_term.png",uca_term, width=6.5, height= 5, units="in",dpi=300)



```












#Ceiling Breaches

```{r QuantileSimpleComp}
df.QCrai.Comp<-ddply(subset(FederalModelAndDetail,
                                        !is.na(Dur.Simple) & 
               !is.na(Ceil.Simple) &
               !is.na(CRai) &
                 !is.na(DecisionTreeDisplay) &
                 !is.na(SingleOffer)
                 ),
      .(DecisionTreeDisplay,
               Ceil.Simple,
               Dur.Simple,
        SingleOffer),
      summarise, 
      crai90 = quantile(pChangeOrderUnmodifiedBaseAndAll, probs = 0.90,na.rm=TRUE), 
      ContractCount=length(CSIScontractID),
      Action.Obligation=sum(Action.Obligation)
      )


df.QCrai.UCA<-ddply(subset(FederalModelAndDetail,
                                        !is.na(Dur.Simple) & 
               !is.na(Ceil.Simple) &
               !is.na(CRai) &
                 !is.na(DecisionTreeDisplay) &
                 !is.na(UCA)
                 ),
      .(DecisionTreeDisplay,
               Ceil.Simple,
               Dur.Simple,
        UCA),
      summarise, 
      crai90 = quantile(pChangeOrderUnmodifiedBaseAndAll, probs = 0.80,na.rm=TRUE), 
      ContractCount=length(CSIScontractID),
      Action.Obligation=sum(Action.Obligation)
      )
df.QCrai.UCA$P

uca80<-ggplot(subset(df.QCrai.UCA,!is.na(UCA)),
       aes(x=DecisionTreeDisplay,y=crai90,color=DecisionTreeDisplay))+
  geom_bar(stat="identity")+
  facet_grid(Dur.Simple~UCA+Ceil.Simple)+
               scale_y_continuous("Cost-Ceiling-Raising Change Orders 80th Percentile (Current $ Value)",
                                  labels=percent)+
  scale_x_discrete("Crisis Dataset or Comparison Group")+
  # scale_linetype_discrete("Early Results")+
  theme(legend.position="none") #, position=pd

ggsave("Output//UCA80.png",uca80,width=6.5, height = 5, units="in", dpi=300)


```
