---
title: "ContractTermination"
author: "Greg Sanders"
date: "Wednesday, February 8, 2017"
output:
  html_document:
    keep_md: yes
--- 

Is Terminated exploration
============================================================================

#Setup
```{r InputFiles, echo = TRUE}
Path<-"C:\\Users\\gsand_000.ALPHONSE\\Documents\\Development\\R-scripts-and-data\\"
# Path<-"D:\\Users\\Greg Sanders\\Documents\\Development\\R-scripts-and-data\\"
# Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(file.path(Path,"lookups.r",sep=""))
source(file.path(Path,"helper.r",sep=""))

source("ContractCleanup.r")
library(csis360)

library(ggplot2)
library(scales)
library(Hmisc)
library(plyr)
Coloration<-read.csv(
    paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
    header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
    stringsAsFactors=FALSE
    )

Coloration<-ddply(Coloration
                  , c(.(R), .(G), .(B))
                  , transform
                  , ColorRGB=as.character(
                      if(min(is.na(c(R,G,B)))) {NA} 
                      else {rgb(max(R),max(G),max(B),max=255)}
                      )
                  )



```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations


Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  


##Prepare Data

```{r ReadInData, echo = TRUE}
load(file="LargeDataSets/Federal_contract_CSIScontractID_detail.Rdata")
head(FederalModelAndDetail)
```

```{r PrepareData}


#ContractWeighted <- apply_lookups(Path,ContractWeighted)


FederalModelAndDetail$TermNum<-as.integer(as.character(factor(FederalModelAndDetail$Term,
                                  levels=c("Terminated","Unterminated"),
                                  labels=c(1,0))))

FederalModelAndDetail$ObligationWT<-FederalModelAndDetail$Action.Obligation
FederalModelAndDetail$ObligationWT[FederalModelAndDetail$ObligationWT<0]<-NA

# FederalModelAndDetail<-ddply(FederalModelAndDetail,
#                          .(Ceil),
#                          
#                          plyr::mutate,
#                          ceil.median.wt = median(UnmodifiedContractBaseAndAllOptionsValue)
# )


FederalModelAndDetail$UnmodifiedYearsFloat<-FederalModelAndDetail$UnmodifiedDays/365.25
FederalModelAndDetail$UnmodifiedYearsCat<-floor(FederalModelAndDetail$UnmodifiedYearsFloat)
FederalModelAndDetail$Dur[FederalModelAndDetail$UnmodifiedYearsCat<0]<-NA

FederalModelAndDetail$Dur.Simple<-as.character(FederalModelAndDetail$Dur)
FederalModelAndDetail$Dur.Simple[FederalModelAndDetail$Dur.Simple %in% c(
    "[0 months,~2 months)",
    "[~2 months,~7 months)",
    "[~7 months-~1 year]")]<-"<~1 year"
FederalModelAndDetail$Dur.Simple<-factor(FederalModelAndDetail$Dur.Simple,
                                          levels=c("<~1 year",
                                               "(~1 year,~2 years]",
                                               "(~2 years+]"),
                                   ordered=TRUE
                                   )

FederalModelAndDetail$Ceil.Simple<-as.character(FederalModelAndDetail$Ceil)

FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "75m+",
    "[75m+]",
    "[10m,75m)",
    "10m - <75m"
    )]<-"10m+"
FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "1m - <10m",
    "[1m,10m)",
    "100k - <1m",
    "[100k,1m)",
    "[100k,1m)"
    )]<-"100k - <10m"
FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "15k - <100k",
    "[15k,100k)",
    "0 - <15k",
    "[0,15k)")]<-"0k - <100k"
FederalModelAndDetail$Ceil.Simple<-factor(FederalModelAndDetail$Ceil.Simple,
       levels=c("0k - <100k",
                "100k - <10m",
                "10m+"),
       ordered=TRUE
       )

FederalModelAndDetail$DecisionTree<-as.character(FederalModelAndDetail$MaxOfDecisionTree)
FederalModelAndDetail$DecisionTree[
  FederalModelAndDetail$DecisionTree=="Excluded"|
    is.na(FederalModelAndDetail$DecisionTree)]<-"All Other"
FederalModelAndDetail$DecisionTree<-factor(FederalModelAndDetail$DecisionTree,levels=c("OCO","Disaster","ARRA","All Other"))
write.csv(subset(FederalModelAndDetail,Term=="Terminated"),"LargeDataSets//Terminated.csv")

```


#Analysis


```{r SDurSCeilCount, fig.width=3,fig.height=9, dpi=600}
TerminatedSDurSCeilStatCount<-ddply(
    subset(FederalModelAndDetail,
           !is.na(Dur.Simple) & 
               !is.na(Ceil.Simple) &
               !is.na(Term) &
               StartFiscalYear>=2007 & 
               StartFiscalYear<=2015 ),
           # &                
           #     (LastCurrentCompletionDate<=as.Date("2015-09-30") |
           #          IsClosed==1) &
           #     UnmodifiedCurrentCompletionDate<as.Date("2015-09-30")),
    .(Dur.Simple,
      Ceil.Simple,
      StartFiscalYear,
      Term,
      DecisionTree,
      Who,
      Intl,
      SinglerOffer,
      UCA
    ),
    plyr::summarise,
    Action.Obligation=sum(Action.Obligation),
    Count=length(CSIScontractID),
    metric="Contracts within Period"
)

TerminatedSDurSCeilStatCount$Period[TerminatedSDurSCeilStatCount$StartFiscalYear>=2007 &
                                      TerminatedSDurSCeilStatCount$StartFiscalYear<=2011]<-
  "2007-2011"
TerminatedSDurSCeilStatCount$Period[TerminatedSDurSCeilStatCount$StartFiscalYear>=2007 &
                                      TerminatedSDurSCeilStatCount$StartFiscalYear<=2011]<-
  "2012+"


TerminatedSDurSCeilStatCount$Term<-factor(TerminatedSDurSCeilStatCount$Term,
                                          levels=c("Unterminated",
                                                   "Terminated"),
                                          labels=c("Unterminated",
                                                   "Complete or Partial Termination"),
                                            ordered=TRUE)


TerminatedSDurSCeilLabels<-ddply(
    subset(TerminatedSDurSCeilStatCount,metric=="Contracts within Period"),
    .(Dur.Simple,Ceil.Simple),
    plyr::summarise,
    FacetCount=paste("Count:",prettyNum(sum(Count),big.mark=",")),
    FacetValue=paste(FacetCount,"\nObligated: $",round(sum(Action.Obligation)/1000000000,1),"B",sep="")
    )

Ypos<-max(TerminatedSDurSCeilStatCount$Count)

TopLineTerm<-LatticePlotWrapper(
  VAR.color.legend.label="Classification",
  VAR.main.label="",
  VAR.X.label="Fiscal Year",
  VAR.Y.label="Constant ($ Billions)",
  VAR.Coloration=Coloration,
  VAR.long.DF=TerminatedSDurSCeilStatCount,
  # NA, #VAR.ncol
  VAR.x.variable="StartFiscalYear", #VAR.x.variable
  VAR.y.variable="Count", #VAR.y.variable
  VAR.y.series="Term", #VAR.y.series
  VAR.facet.primary="Dur.Simple", #VAR.facet.primary
  VAR.facet.secondary= "Ceil.Simple", # VAR.facet.secondary=NA
  # ,MovingAverage=0
  # ,MovingSides=1
  DataLabels=FALSE
  #                       ,VAR.override.coloration=NA
)+geom_text(data=TerminatedSDurSCeilLabels,
              aes(x=2007,y=Ypos,label=FacetValue),
              # parse=TRUE,
              hjust=0,
              vjust=1,
              color="black")

# ggplot(TerminatedSDurSCeilStatCount,
#        aes(x=StartFiscalYear,y=Count,color=Term))+
#     geom_line(aes(linetype=metric))+
#     geom_point(aes(shape=Term))+
#     geom_text(data=TerminatedSDurSCeilLabels,
#               aes(x=2007,y=Ypos,label=FacetValue),
#               # parse=TRUE,
#               hjust=0,
#               vjust=1,
#               color="black")+
#     facet_grid( Dur.Simple  ~ Ceil.Simple ) +#
#     scale_x_continuous("Contract Starting Fiscal Year")+
#     scale_color_manual("Status", values=c("blue","red"))+
#     scale_linetype_discrete("Early Results")+
#     scale_shape_discrete("Status")+
#     scale_y_log10("Number of Contracts (Logorithmic Scale)",label=comma)+
#     # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1)+
#     theme(legend.position="bottom") #, position=pd


```

