---
title: "ContractTermination"
author: "Greg Sanders"
date: "Wednesday, February 8, 2017"
output:
  html_document:
    keep_md: yes
--- 

Is Terminated exploration
============================================================================

#Setup
```{r InputFiles, echo = TRUE}


Path<-"C:\\Users\\gsand_000.ALPHONSE\\Documents\\Development\\R-scripts-and-data\\"
# Path<-"D:\\Users\\Greg Sanders\\Documents\\Development\\R-scripts-and-data\\"
# Path<-"K:\\2007-01 PROFESSIONAL SERVICES\\R scripts and data\\"
source(file.path(Path,"lookups.r",sep=""))
source(file.path(Path,"helper.r",sep=""))

source("ContractCleanup.r")

library(ggplot2)
library(scales)
library(Hmisc)
library(plyr)
Coloration<-read.csv(
    paste(Path,"Lookups\\","lookup_coloration.csv",sep=""),
    header=TRUE, sep=",", na.strings="", dec=".", strip.white=TRUE, 
    stringsAsFactors=FALSE
    )

Coloration<-ddply(Coloration
                  , c(.(R), .(G), .(B))
                  , transform
                  , ColorRGB=as.character(
                      if(min(is.na(c(R,G,B)))) {NA} 
                      else {rgb(max(R),max(G),max(B),max=255)}
                      )
                  )



```

Contracts are classified using a mix of numerical and categorical variables. While the changes in numerical variables are easy to grasp and summarize, a contract may have one line item that is competed and another that is not. As is detailed in the exploration on R&D, we are only considering information available prior to contract start. The percentage of contract obligations that were competed is a valuable benchmark, but is highly influenced by factors that occured after contract start..

## Contract Terminations


Contract terminations and the number of change orders can be calculated for the entire sample.  Contract termination is determined using the *Reason for Modification* field in FPDS.  A contract is considered to be terminated if it has at least one modification with the following values:

* "Terminate for Default (complete or partial)"
* "Terminate for Convenience (complete or partial)"
* "Terminate for Cause"
* "Legal Contract Cancellation"

These four catetegories and the "Close Out" category are used to mark a contract as closed.  Many contracts in FPDS and in the sample are never marked closed.  


##Prepare Data

```{r ReadInData, echo = TRUE}
load(file="LargeDataSets/Federal_contract_CSIScontractID_detail.Rdata")
head(FederalModelAndDetail)

debug(FormatContractModel)
FederalModelAndDetail<-FormatContractModel(FederalModelAndDetail)




#ContractWeighted <- apply_lookups(Path,ContractWeighted)


FederalModelAndDetail$TermNum<-as.integer(as.character(factor(FederalModelAndDetail$Term,
                                  levels=c("Terminated","Unterminated"),
                                  labels=c(1,0))))

FederalModelAndDetail$ObligationWT<-FederalModelAndDetail$Action.Obligation
FederalModelAndDetail$ObligationWT[FederalModelAndDetail$ObligationWT<0]<-NA

FederalModelAndDetail<-ddply(FederalModelAndDetail,
                         .(Ceil),
                         
                         plyr::mutate,
                         ceil.median.wt = median(UnmodifiedContractBaseAndAllOptionsValue)
)


FederalModelAndDetail$UnmodifiedYearsFloat<-FederalModelAndDetail$UnmodifiedDays/365.25
FederalModelAndDetail$UnmodifiedYearsCat<-floor(FederalModelAndDetail$UnmodifiedYearsFloat)
FederalModelAndDetail$Dur[FederalModelAndDetail$UnmodifiedYearsCat<0]<-NA

FederalModelAndDetail$Dur.Simple<-as.character(FederalModelAndDetail$Dur)
FederalModelAndDetail$Dur.Simple[FederalModelAndDetail$Dur.Simple %in% c(
    "[0 months,~2 months)",
    "[~2 months,~7 months)",
    "[~7 months-~1 year]")]<-"<~1 year"
FederalModelAndDetail$Dur.Simple<-factor(FederalModelAndDetail$Dur.Simple,
                                          levels=c("<~1 year",
                                               "(~1 year,~2 years]",
                                               "(~2 years+]"),
                                   ordered=TRUE
                                   )

FederalModelAndDetail$Ceil.Simple<-as.character(FederalModelAndDetail$Ceil)

FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "75m+",
    "10m - <75m")]<-"10m+"
FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "1m - <10m",
    "100k - <1m")]<-"100k - <10m"
FederalModelAndDetail$Ceil.Simple[FederalModelAndDetail$Ceil.Simple %in% c(
    "15k - <100k",
    "0 - <15k")]<-"0k - <100k"
FederalModelAndDetail$Ceil.Simple<-factor(FederalModelAndDetail$Ceil.Simple,
       levels=c("0k - <100k",
                "100k - <10m",
                "10m+"),
       ordered=TRUE
       )




write.csv(subset(FederalModelAndDetail,Term=="Terminated"),"Terminated.csv")

```

**A Histogram of the IsTerminated data** showing the distribution of whether or not a contract was terminated each year from 2007.  

```{r ContractTerminationGraphs, echo = TRUE, fig.width=3,fig.height=9, dpi=600}
# TerminatedDurSummary<-ddply(subset(FederalModelAndDetail,StartFiscalYear>=2007 & 
#                   !is.na(Ceil)&
#                   UnmodifiedCompletionDate<=as.Date("2015-09-30")&
#                       !is.na(Term)),
#                             .(Ceil,
#                               Dur,
#                               StartFiscalYear,
#                               Term
#                             ),
#                             plyr::summarise,
#                             Action.Obligation=sum(Action.Obligation),
#                             Count=length(CSIScontractID)
#                   )
# 
# 
# TerminatedDurSummary<-ddply(TerminatedDurSummary,.(Ceil,
#                                                   Dur,
#                                              StartFiscalYear
#                                              ),transform,
#                       pContractCeilDurStart=Count/sum(Count),
#                       pObligationCeilDurStart=Action.Obligation/sum(Action.Obligation)
#       )
# 
# 
# ggplot(TerminatedDurSummary,
#        aes(x=StartFiscalYear,
#            y=Count,
#            color=Term))+geom_line()+    geom_point(aes(shape=metric))+facet_grid(Ceil ~ Dur ) +scale_y_log10(labels=scales::comma)
# 
# 
# 
# 
# 
# 
# ggplot(
#   data = TerminatedEndSummary,
#   aes_string(x = "Term"),
#   ) + geom_bar() + 
#     facet_grid( Ceil ~ .,
#                 scales = "free_y",
#                 space = "free_y") + scale_y_continuous(expand = c(0,50)) 
# 
# 
# 
# 
# 
# ggplot(
#   data = subset(TerminatedEndSummary,Term=="Terminated"),
#   aes_string(x = "Ceil")
#   )+ geom_bar()+
#     scale_x_discrete("Original Ceiling (Current $ Value)")+scale_y_continuous("Number of Partially or Completely \nTerminated Contracts",labels = comma)+theme(axis.text.x=element_text(angle=90,size=12))
# 
# 
# 
# 
# 
# 
# TerminatedEndSummary$Graph[TerminatedEndSummary$Term=="Terminated"]<-TRUE
# 
# TerminatedEndSummary$Graph[TerminatedEndSummary$Term=="Unterminated"]<-FALSE
# 
# 
# head(TerminatedEndSummary)
# 
# ggplot(
#   data = subset(TerminatedEndSummary,Term=="Terminated"),
#   aes(x = Ceil,weight=Action.Obligation/1000000000)
#   )+ geom_bar()+
#     scale_x_discrete("Original Ceiling (Current $ Value)")+scale_y_continuous("Obligations to Partially or Completely\nTerminated Contracts (Current $ Billions)",labels = comma)+theme(axis.text.x=element_text(angle=90,size=12))
# 
# 
# ggplot(
#   data = subset(TerminatedEndSummary,Term=="Terminated"),
#   aes_string(x = "Ceil",weight="pContract")
# #   main="Percentage of Contracts going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
#   )+ geom_bar()+ scale_y_continuous("Percent of Contracts Partially or Completely Terminated\nby Original Ceiling Category", labels=percent)+
#     scale_x_discrete("Original Ceiling (Current $ Value)")+theme(axis.text.x=element_text(angle=90,size=12))
# 
# 
# ggplot(
#   data = subset(TerminatedEndSummary,Term=="Terminated"),
#   aes_string(x = "Ceil",weight="pObligation"),
#   main="Percentage of Contract Obligations going to Partially or Completely Terminated Contracts\nBy Initial Contract Ceiling"
#   )+ geom_bar()+ scale_y_continuous("Percent of Obligations to Terminated Contracts \nin Original Ceiling Category", labels=percent)+
#     scale_x_discrete("Original Ceiling (Current $ Value)")+theme(axis.text.x=element_text(angle=90,size=12))
# 
# 
# # 
# # LatticePercentLineWrapper("VAR.name"
# #                                     ,"VAR.proper.name"
# #                                     ,"VAR.X.label"
# #                                     ,"VAR.Y.label"
# #                                     ,Coloration
# #                                     ,subset(TerminatedEndSummary,!is.na(Term))
# #                                     ,NULL
# #                                     ,"Ceil"
# #                                     ,"Count"
# #                                     ,"Term"
# #                                     ,NA
# #                                     ,NA
# #                                     )
# 
# # 
# # + 
# #     facet_grid( Ceil ~ .,
# #                 scales = "free_y",
# #                 space = "free_y") 
# # 

```




```{r SDurSCeilCount, fig.width=3,fig.height=9, dpi=600}
TerminatedSDurSCeilStatCount<-ddply(
    subset(FederalModelAndDetail,
           !is.na(Dur.Simple) & 
               !is.na(Ceil.Simple) &
               !is.na(Term) &
               StartFiscalYear>=2007 & 
               StartFiscalYear<=2014 &                
               (LastCurrentCompletionDate<=as.Date("2015-09-30") |
                    IsClosed==1) &
               UnmodifiedCurrentCompletionDate<as.Date("2015-09-30")),
    .(Dur.Simple,
      Ceil.Simple,
      StartFiscalYear,
      Term
    ),
    plyr::summarise,
    Action.Obligation=sum(Action.Obligation),
    Count=length(CSIScontractID),
    metric="Contracts within Period"
)

TerminatedSDurSCeilStatCount<-rbind(TerminatedSDurSCeilStatCount,
                                    ddply(subset(FederalModelAndDetail,
                                           !is.na(Dur.Simple) & 
                                               !is.na(Ceil.Simple) &
                                               !is.na(Term) &
                                               StartFiscalYear>=2007 & 
                                               StartFiscalYear<=2014),               
                                    .(Dur.Simple,
                                      Ceil.Simple,
                                      StartFiscalYear,
                                      Term
                                    ),
                                    plyr::summarise,
                                    Action.Obligation=sum(Action.Obligation),
                                    Count=length(CSIScontractID),
                                    metric="Early Results for All Contracts"
)
)
TerminatedSDurSCeilStatCount$metric<-factor(TerminatedSDurSCeilStatCount$metric,
                                            levels=c("Contracts within Period",
                                                   "Early Results for All Contracts"),
                                            ordered=TRUE)

TerminatedSDurSCeilStatCount$Term<-factor(TerminatedSDurSCeilStatCount$Term,
                                          levels=c("Unterminated",
                                                   "Terminated"),
                                          labels=c("Unterminated",
                                                   "Complete or Partial Termination"),
                                            ordered=TRUE)


TerminatedSDurSCeilLabels<-ddply(
    subset(TerminatedSDurSCeilStatCount,metric=="Contracts within Period"),
    .(Dur.Simple,Ceil.Simple),
    plyr::summarise,
    FacetCount=paste("Count:",prettyNum(sum(Count),big.mark=",")),
    FacetValue=paste(FacetCount,"\nObligated: $",round(sum(Action.Obligation)/1000000000,1),"B",sep="")
    )

Ypos<-max(TerminatedSDurSCeilStatCount$Count)


ggplot(TerminatedSDurSCeilStatCount,
       aes(x=StartFiscalYear,y=Count,color=Term))+
    geom_line(aes(linetype=metric))+
    geom_point(aes(shape=Term))+
    geom_text(data=TerminatedSDurSCeilLabels,
              aes(x=2007,y=Ypos,label=FacetValue),
              # parse=TRUE,
              hjust=0,
              vjust=1,
              color="black")+
    facet_grid( Dur.Simple  ~ Ceil.Simple ) +#
    scale_x_continuous("Contract Starting Fiscal Year")+
    scale_color_manual("Status", values=c("blue","red"))+
    scale_linetype_discrete("Early Results")+
    scale_shape_discrete("Status")+
    scale_y_log10("Number of Contracts (Logorithmic Scale)",label=comma)+
    # geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1)+
    theme(legend.position="bottom") #, position=pd


```

